---
title: "p8105_hw1_jm5509"
author: "Echo"
date: "2022-09-19"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

This a short description of the penguins dataset. The function of str() and 
summary() illustrate the names and values of important variables.

```{r penguins}
data('penguins',package='palmerpenguins')
str(penguins) 
# Shows the length of the tibble, numeric variables and int varibles; 
# and the levels of the factor variables(including species,island and sex)
summary(penguins)
# Shows the number of the factor variables, and basic statistical 
# values of numeric variables

nrow(penguins)
ncol(penguins)

mean(penguins$flipper_length_mm)

library(tidyverse)
ggplot(penguins,aes(x=bill_length_mm,y=flipper_length_mm, color=species))+geom_point()
ggsave('penguins.pdf')
```

## Problem 2

This solution is displayed as follows. In this case, we create a data frame 
comprised of 4 variables with different data types. Among them, only the numeric
and the logical value could be taken the mean value.

```{r dataframe}
library(tidyverse)
df = 
tibble(
norm=rnorm(n=10),
logical=norm>0,
character=c('a','b','c','d','e','f','g','h','i','j'),
factor=as.factor(c(rep('paper',3),rep('scissors',4),rep('rock',3)))
)

mean(df %>% pull(1))
mean(df %>% pull(2))
mean(df %>% pull(3))
mean(df %>% pull(4))

```

We further convert three other variables to numeric ones. It turns out that only 
logical and factor vectors could be converted.
Logical values could be converted from TRUE/FALSE to 1/0. That could explain why
it can be taken the mean value.
Factor values could be converted to its corresponding order when being converted. 
Character values are converted to "NA"s. However, if the character values is 
converted from numeric values, then it could be converted back to numeric values.

```{r asnumeric, eval=FALSE}
as.numeric(df %>% pull(2)) # logical
as.numeric(df %>% pull(3)) # character
as.numeric(df %>% pull(4)) # factor
```